An Imaging Search for Circumstellar Companions of Sirius B

### 2021-10-14 paper/paper.tex
update paper with references and new intro

High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets. Probing the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory. Imaging a planet is challenging, however. The typical astrophysical flux ratios (contrast) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traub_direct_2010}. Thermal emission from exoplanets peaks in the infrared and is well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible or ultraviolet. In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.

Typical targets for imaging are nearby young stars; the proximity means the same angular separation probes a smaller physical separation, allowing for studies closer to solar-system scales. Younger exoplanets are hotter and therefore brighter, reducing the flux ratio between the planet and its host star. Another way to reduce contrast would be to image a faint star with bright companions, such as a young white dwarf (WD) star. When intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) eventually exit the main-sequence (MS) they expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase. This expansion engulfs planets within the star's Roche limit. If the planet survives this expansion, its orbital separation will gradually increase as the star loses mass during the asymptotic giant branch (AGB) phase. Finally, once the star becomes a white dwarf it begins cooling, which will reduce its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor. The faintness, lack of spectral features, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods. However, the reduced contrast due to the faintness of the star, and the expanded separation of planets both benefit imaging.

\section{Post-MS Evolution}

There is limited knowledge of planetary systems around evolved stars. \citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase. Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhaus_orbits_2013}. During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}. In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.

The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983}. They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet. They studied $\sim$100 white dwarfs but found no companions. The same method was applied by \citet{zuckerman_excess_1987}, who found excess IR emission around white dwarf G29-38. The emission was determined to be from a dust disk \citep{telesco_observations_1990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koester_metals_1997}. It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsor_pollution_2015}. \citet{skemer_sirius_2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.

Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf. \citet{luhman_discovery_2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.

\section{Sirius B and the Sirius System}

A particularly fascinating target is Sirius B, the closest and brightest white dwarf. The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}. As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortney_giant_2010}.

@@

The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''. This dark satellite was visually confirmed in \citet{bond_companion_1862} as Sirius B. \citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.

Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwers_orbit_1864}. \citet{van_den_bos_orbit_1960,gatewood_study_1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories. \citet{bond_sirius_2017} greatly refined the orbital solution using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holman_long-term_1999}. \citet{bond_sirius_2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

To find the total age of Sirius B, \citet{bond_sirius_2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first. Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bond_sirius_2017}. An age uncertainty of $\sim$1\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.

The first modern imaging study searching for companions around Sirius B was \citet{schroeder_search_2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}. Around the same time \citet{kuchner_search_2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}. These studies combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}). \citet{bonnet-bidaud_adonis_2008} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reached a sensitivty of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}). \citet{skemer_sirius_2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B. \citet{thalmann_piercing_2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B. Because of the simultaneous observation, their contrast depended on which region of the FOV was tested. Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

@@

\section{Observations} \label{sec:obs}

\begin{deluxetable*}{ccccccccc}
    \tabletypesize{\small}
    \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}). Observation time is based on the frames that were selected for processing. Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
    \label{tbl:obs}}
    \tablehead{
        \colhead{\makecell{Date\\observed}} &
        \colhead{\makecell{Sirius B\\offset} (\unit{\arcsecond})} &
        \colhead{\makecell{Sirius B\\PA} (\unit{\degree})} &
        \colhead{\makecell{Obs.\\time} (hr)} &
        \colhead{\makecell{FOV\\rotation} (\unit{\degree})} &
        \colhead{FWHM (\unit{\milliarcsecond})} &
        \colhead{Seeing (\unit{\arcsecond})} &
        \colhead{Temp (\unit{\celsius})} &
        \colhead{PWV (\unit{\milli\meter})}
    }
    \startdata
    2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & 0.936 & 0.0 & 0.7 \\
    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & 0.871 & 0.8 & 3.5 \\
    2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & 1.23 & -1.5 & 3.0 \\
    \enddata
\end{deluxetable*}

@@

Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes. We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) using the narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) across three epochs in 2020 (\cref{tbl:obs}). Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A. The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS). Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{huby_w_2017}, performed erratically in the presence of the scattered light. We did not try coronagraphy for the remaining observations. \citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE. In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.

The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS. While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop. From here, we slewed off-axis using the separations and position angles calculated in \cref{tbl:obs} from the orbital parameters in \citet{bond_sirius_2017}. In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.

During each observation, we took dark frames and sky-flat frames for calibration. All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{marois_angular_2006}.

@@

\begin{figure*}
    \centering
    \epsscale{1}
    \plotone{contrast_curves}
    \caption{The contrast curves for the best performing algorithm from each epoch. The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves. The mean uncertainty from the total system age ($\sim$\qty{10}{\mega\year}) is shown by a lone error bar. In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line. The companion mass values are interpolated from the AMES-Cond grid. The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line. The annular PCA curve is cut off because the innermost annulus had greater than 1 contrast, which is invalid.}
    \label{fig:contrast}
\end{figure*}

@@

The raw images from NIRC2 required pre-processing before analyzing them for companions. For each epoch, we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \cref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.

The co-registered frames were shifted to the center of the FOV and cropped to the inner 200 pixels. With a pixel scale of \qty{10}{\milliarcsecond} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}. All the frames were stacked into data cubes for each epoch. We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yelda_improving_2010}. For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\cref{fig:psf}). All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}) and the pre-processed data cubes and parallactic angles are available on Zenodo:\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}.

@@

By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate. This reduces the probability of removing companion signal when we subtract the stellar PSF model. After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.

>>>>

High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets. Probing the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory. Imaging a planet is challenging, however. The typical astrophysical flux ratios (contrast) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}. Thermal emission from exoplanets peaks in the infrared and is well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible or ultraviolet. In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.

White dwarfs (WD) are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their main-sequence (MS) progenitors which reduces the contrast necessary to detect a companion. In addition, the relative lack of spectral features of WDs makes them imprecise targets for radial velocity analysis. The intrinsic faintness of WDs proves challenging for all detection methods; this is exacerbated on ground-based telescopes which require significant signal-to-noise (S/N) to operate their adaptive optics (AO) facilities. This implicitly limits searches of WDs to the $\sim$\qty{100}{\parsec} neighborhood. Little is known about post-MS planetary evolution, however, planets that are tenuous enough to survive the red giant and asymptotic giant phases of its host are interesting laboratories for planetary formation pathways as showcased by recent discoveries like giant planet candidate WD 1856+534b \citep{vanderburgGiantPlanetCandidate2020}.

In this work, we briefly review post-MS planetary formation theory (\cref{sec:post-ms}) and discuss the Sirius system, specifically bright WD Sirius B, as potential exoplanet hosts (\cref{sec:sirius}). In \cref{sec:obs}, \cref{sec:analysis}, and \cref{sec:results} we describe our observations of Sirius B in 2020, along with the subsequent analysis. Finally, in \cref{sec:conclusion} we discuss the implications of our observations for planetary formation theory and future work.

\section{Post-MS Evolution} \label{sec:post-ms}

There is limited knowledge of planetary systems around evolved stars. \citet{burleighImagingPlanetsNearby2002a,verasPostmainsequencePlanetarySystem2016} suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase. Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhausOrbitsLowmassCompanions2013}. During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeansCosmogonicProblemsAssociated1924}. In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{peretsSecondGenerationPlanets2010}.

The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}. They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet. They studied $\sim$100 white dwarfs but found no companions. The same method was applied by \citet{zuckermanAncientPlanetarySystems2010}, who found excess IR emission around white dwarf G29-38. The emission was determined to be from a dust disk \citep{telescoObservationsG29381990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koesterMetalsVariableG29381997}. It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsorInfraredObservationsWhite2017}. \citet{skemerSiriusImagedMidinfrared2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.

Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf. \citet{luhmanDiscoveryCandidateCoolest2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hoganDODOSurveyII2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xuExtremeAOSearchGiant2015a}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.

\section{Sirius B and the Sirius System} \label{sec:sirius}

A particularly fascinating target is Sirius B, the closest and brightest white dwarf. The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}. As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.

@@

The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{besselVariationsProperMotions1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''. This dark satellite was visually confirmed in \citet{bondCompanionSiriusProf1862} as Sirius B. \citet{adamsSpectrumCompanionSirius1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.

Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}. \citet{vandenbosOrbitSiriusADS1960,gatewoodStudySirius1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories. \citet{bondSiriusSystemIts2017} greatly refined the orbital solution using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

To find the total age of Sirius B, \citet{bondSiriusSystemIts2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first. Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummingsTwoMassiveWhite2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bondSiriusSystemIts2017}. An age uncertainty of $\sim$1\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.

The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}. Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}. These studies combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}). \citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reached a sensitivty of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}). \citet{skemerSiriusImagedMidinfrared2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B. \citet{thalmannPiercingGlareDirect2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Recently, \citet{pathakHighContrastImaging2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B. Because of the simultaneous observation, their contrast depended on which region of the FOV was tested. Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

@@

\section{Observations} \label{sec:obs}
\defcitealias{bonnet-bidaudADONISHighContrast2008a}{BB08}
\defcitealias{bondSiriusSystemIts2017}{B17}
\defcitealias{collaborationGaiaEarlyData2021a}{G21a}
\defcitealias{cummingsWhiteDwarfInitialFinal2018}{C18}
\begin{deluxetable}{cccc}
    \tablecaption{Parameters of the Sirius system adopted in this study.\label{tbl:system}}
    \tablehead{
        \colhead{parameter} & \colhead{value} & \colhead{unit} & \colhead{ref.}
    }
    \startdata
    $t_\mathrm{sys}$ & 226 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
    $\pi$ & \num{374.5\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
    $d$ & \num{2.67\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
    \cutinhead{Sirius A}
    $M_\star$ & \num{2.063\pm0.023} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
    \cutinhead{Sirius B}
    $M_\star$ & \num{1.018\pm0.011} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
    $t_\mathrm{WD}$ & 125 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018}\\
    $m^{Lp}$ & \num{9.01\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
    $M^{Lp}$ & \num{11.88\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
    \enddata
\end{deluxetable}

\begin{deluxetable*}{ccccccccc}[t]
    \tabletypesize{\small}
    \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}). Observation time is based on the frames that were selected for processing. Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
    \label{tbl:obs}}
    \tablehead{
        \colhead{\makecell{Date\\observed}} &
        \colhead{\makecell{Sirius B\\offset} (\unit{\arcsecond})} &
        \colhead{\makecell{Sirius B\\PA} (\unit{\degree})} &
        \colhead{\makecell{Obs.\\time} (hr)} &
        \colhead{\makecell{FOV\\rotation} (\unit{\degree})} &
        \colhead{FWHM (\unit{\milliarcsecond})} &
        \colhead{Seeing (\unit{\arcsecond})} &
        \colhead{Temp (\unit{\celsius})} &
        \colhead{PWV (\unit{\milli\meter})}
    }
    \startdata
    2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & 0.936 & 0.0 & 0.7 \\
    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & 0.871 & 0.8 & 3.5 \\
    2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & 1.23 & -1.5 & 3.0 \\
    \enddata
\end{deluxetable*}

% \begin{deluxetable}{ccccc}
%     \tabletypesize{\small}
%     \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}). Observation time is based on the frames that were selected for processing. Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
%     \label{tbl:obs}}
%     \tablehead{
%         \colhead{Epoch} &
%         \colhead{2020-02-4} &
%         \colhead{2020-11-21} &
%         \colhead{2020-11-28} &
%         \colhead{}
%     }
%     \startdata
%     Sirius B offset & 11.20 & 11.27 & 11.27 & \unit{\arcsecond}  \\
%     Sirius B PA & 67.90 & 66.42 & 66.38 & \unit{\degree} \\
%     Obs. time & 1.44 & 2.91 & 2.44 & hr \\
%     FOV rotation & 60.1 & 91.4 & 80.4 & \unit{\degree} \\
%     FWHM & 79.9 & 76.4 & 82.2 & \unit{\milliarcsecond} \\
%     Seeing & 0.936 & 0.871 & 1.23 & \unit{\arcsecond} \\
%     Temp & 0.0 & 0.8 & -1.5 & \unit{\celsius} \\
%     PWV & 0.7 & 3.5 & 3.0 & \unit{\milli\meter}
%     \enddata
% \end{deluxetable}

@@

Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes. We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) using the narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) across three epochs in 2020 (\cref{tbl:obs}). Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A. The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS). Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabynKeckObservatoryInfrared2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{hubyOnskyPerformanceQACITS2017a}, performed erratically in the presence of the scattered light. We did not try coronagraphy for the remaining observations. \citet[\S2]{viganHighcontrastImagingSirius2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE. In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.

The Keck AO system \citep{wizinowichPerformanceKeckObservatory2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS. While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop. From here, we slewed off-axis using the separations and position angles calculated in \cref{tbl:obs} from the orbital parameters in \citet{bondSiriusSystemIts2017}. In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.

During each observation, we took dark frames and sky-flat frames for calibration. All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.

@@

\begin{figure*}
    \centering
    \epsscale{1}
    \plotone{contrast_curves}
    \caption{The contrast curves for the best performing algorithm from each epoch. The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves. The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line. The annular PCA curve is cut off because the innermost annulus has a contrast value greater than 1, which means even a 100 S/N companion would not be detectable with 5$\sigma$ significance.}
    \label{fig:contrast}
\end{figure*}

\begin{figure*}
    \centering
    \epsscale{1}
    \plotone{mass_curves}
    \caption{Mass sensitivity curves derived from the 2020-11-21 epoch, which has the best contrast. The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits. The two ages represent the ages of the two potential formation pathways, one of which is the system age (\qty{226}{\mega\year}), the other is the WD cooling age of Sirius B (\qty{125}{\mega\year}). The limits are calculated assuming an Lp apparant magnitude for Sirius B of \num{9.01} and converting contrast into absolute magnitudes. The absolute magnitudes are converted to masses using the ATMO2020 isochrone grid with non-equilibrium chemistry and weak convective mixing. The lower mass limit of the ATMO2020 grid is plotted with a horizontal dashed line and the expected upper limit for dynamically stable orbits of \qty{1.5}{\au} is plotted with a vertical dashed line.}
    \label{fig:mass}
\end{figure*}

@@

The raw images from NIRC2 required pre-processing before analyzing them for companions. For each epoch, we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{vandokkumCosmicRayRejectionLaplacian2001a} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \cref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.

The co-registered frames were shifted to the center of the FOV and cropped to the inner 200 pixels. With a pixel scale of \qty{10}{\milliarcsecond} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}. All the frames were stacked into data cubes for each epoch. We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yeldaImprovingGalacticCenter2010}. For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\cref{fig:psf}). All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\cref{sec:data}).

@@

By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate. This reduces the probability of removing companion signal when we subtract the stellar PSF model. After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
